Ensemble Stability of Biological Networks

### 2014-09-16 paper.tex
add results sections

\section{Two component systems}
For two-component systems having $2 \times 2$ Jacobian matrices, the aforementioned stability criteria result in the conditions $T < 0$ and $D >
0$ where $T$ and $D$ denote the trace and the determinant.

@@

The probability of \emph{a priori} stability and of stability to perturbations for all two component systems is given in Table \ref{tab:structstabmat}.

\section{Three component systems}

The probability of \emph{a priori} stability and of stability to perturbations for all three component systems is given in Table \ref{tab:structstabmat3}. \ref{fig:connectcycle3D3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity and number of cycles. \ref{fig:stab3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity. \ref{fig:cycle3x3} shows the probability of stability to perturbations for all three component systems as a function of the number of simple cycles (elementary circuits) of length greater than one in the corresponding directed graph \cite{Johnson1975}.

>>>>

\section{Stability and robustness analysis of multi-component systems}
For two-component systems having $2 \times 2$ Jacobian matrices, the aforementioned stability criteria result in the conditions $T < 0$ and $D >
0$ where $T$ and $D$ denote the trace and the determinant.

@@

The probability of \emph{a priori} stability and of stability to perturbations for all two component systems is given in Table \ref{tab:structstabmat}. Similarly, the analogous results for all three component systems is given in Table \ref{tab:structstabmat3}.

\section{Connectivity is correlated with robustness}
\ref{fig:stab3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity.

\section{Cycle number is inversely correlated with robustness}
\ref{fig:cycle3x3} shows the probability of stability to perturbations for all three component systems as a function of the number of simple cycles (elementary circuits) of length greater than one in the corresponding directed graph \cite{Johnson1975}.

\section{Cycle number and connectivity classify robust systems}
\ref{fig:connectcycle3D3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity and number of cycles.

\section{Hierarchical systems are the most robust}
\ref{fig:scc} shows systems with varying levels of hierarchy and modularity.

\section{Discussion}
